The finite representation property for some reducts of relation algebras

### 2021-05-30 filtration-stuff/NewText.tex
filtrations for K5 * K5

\documentclass[a4paper]{article}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{bussproofs}
\usepackage{mathtools}
\usepackage{verbatim}
\usepackage{dsfont}
\usepackage{mathabx}
\usepackage[all, 2cell]{xy}
\usepackage[all]{xy}
\usepackage{wasysym}
\usepackage{rotating}
\usepackage{geometry}
\usepackage{trfsigns}
\usepackage{cmll}
\usepackage{authblk}
\usepackage{hyperref}
\usepackage{cleveref}
\usepackage{lipsum}
\usepackage{extpfeil}
\usepackage{soul}
\usepackage{graphicx}

@@

  \xymatrix{
  &&&&&&& w_5\ar@(ul,ur) \ar@<-.5ex>[d] \\
  &&&&&& w_1\ar@(ul,ur)  & w_4 \ar@<.5ex>[u] \ar@(dl,ul)^{} \\
  &&&&&& w_2 \ar[u] & w_3 \ar[u]
  }
\end{proof}

@@

@@

The converse implication does not have to true generally.

Recall that ${\bf GL} = {\bf K} \oplus \Diamond (p \land \neg \Diamond p) \to \Diamond p$. ${\bf GL}$ does not admit filtrations, but one may prove that ${\bf GL}$ has the FMP using the selective filtation technique.

\begin{defin}
  Let $\mathcal{M} = \langle W, R, \vartheta \rangle$ be a model and $\Gamma$ a set closed under subformulas, then a weak submodel $\mathcal{M} = \langle W', R', \eta \rangle$ (that is, $W' \subseteq W$, $R' \subseteq R$, $\eta = \vartheta \upharpoonright_{W'}$) is called a selective filtration of $\mathcal{M}$ through $\Gamma$ is the following holds, for $\Diamond \psi \in \Gamma$, $x \in W'$:
  \begin{center}
    $\mathcal{M}, x \models \Diamond \psi$ iff $\mathcal{M}, y \models \psi$ for some $y \in R'(x)$
  \end{center}
\end{defin}

\begin{theorem}
  ${\bf GL}$ admits the ``finite canonical'' model property.
\end{theorem}

\begin{proof}
  Let $\Gamma$ be a finite $\operatorname{\bf Sub}$-closed set. So, $\Gamma = \operatorname{\bf Sub}(\gamma_1) \cup \dots \operatorname{\bf Sub}(\gamma_n)$, for some $\gamma_1, \dots, \gamma_n \in \Gamma$ and every $\gamma_i$ is ${\bf GL}$-consistent.

  $\gamma$ is true in $\mathcal{M}_{\Gamma} = \langle V, R^{\bf GL}, \vartheta \rangle$, where
  \begin{center}
  $V_{\Gamma} = \bigcup \limits_{\psi \in \Gamma} \{ x \in W_{\bf GL} \: | \: \mathcal{M}_{\bf GL}, x \models \psi \land \neg \Diamond \psi \}$
  \end{center}
  since $\mathcal{M}_{\Gamma}$ is a selective filtration of $\mathcal{M}_{\bf M}$ through $\Gamma$.

  Let $x \in V$, consider $||x|| = \{ \psi \in \Gamma \: | \: \mathcal{M}_{\bf GL}, x \models \psi \}$
  and define $x R^{\bf GL} y$ implies $||x|| R_{\Gamma} ||y||$. Every $||x||$ is clearly finite.
  The valuation map is usual, $\vartheta_{\Gamma}(p) = \{ ||x|| \: | \: p \in ||x|| \}$ for $p \in \operatorname{PV} \cap \Gamma$. We put $W_{\Gamma}$

  Let us check that $\langle W_{\Gamma}, R_{\Gamma}, \vartheta_{\Gamma} \rangle$ is a ``finite canonical`` ${\bf GL}$-model.
  Let us check that $R_{\Gamma}$ is transitive and Noetherian and it has no relflexive points.
  If $W_{\Gamma}$ had a relfexive point, say $||y||$, then we would have $\mathcal{M}, y \models \psi \to \Diamond \psi$, but that is not impossible. Transitivity is obvious.

  Clearly that $x R^{\bf GL} y$ implies $||x|| R_{\Gamma} ||y||$ and vice versa. So, if we had an infinite decreasing $R_{\Gamma}$-chain, then we would have an infinite decreasing $R^{\bf GL}$-chain, but that is not possible.
  So $\langle W_{\Gamma}, R_{\Gamma}, \vartheta_{\Gamma} \rangle$ is a ``finite canonical`` ${\bf GL}$-model.
\end{proof}

So we have an example of a logic that has the ``finite canonical'' model property with no filtrations.

>>>>

\documentclass[a4paper]{article}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{bussproofs}
\usepackage{mathtools}
\usepackage{verbatim}
\usepackage{dsfont}
\usepackage{mathabx}
\usepackage[all, 2cell]{xy}
\usepackage[all]{xy}
\usepackage{wasysym}
\usepackage{rotating}
\usepackage{geometry}
\usepackage{trfsigns}
\usepackage{cmll}
\usepackage{authblk}
\usepackage{hyperref}
\usepackage{cleveref}
\usepackage{lipsum}
\usepackage{extpfeil}
\usepackage{soul}
\usepackage{graphicx}
\usepackage{wasysym}

@@

  \xymatrix{
  &&&&&&& w_5\ar@(ul,ur) \ar@<-.5ex>[d] \\
  &&&&&& w_1\ar@(ul,ur)  & w_4 \ar@<.5ex>[u] \ar@(dl,ul)^{} \\
  &&&&&& w_2 \ar[u] & w_3 \ar[u]
  }

@@

\end{proof}

Let us define the logic $\mathcal{L}$ as ${\bf K} \oplus \Diamond \Diamond \Diamond p \to \Diamond p$. Let $R$ be a binary relation, the $\mathcal{L}$-closure of $R$ is defined (denoted as $R^{\davidsstar}$) as the following union:
\begin{center}
  $R^{\davidsstar} = R \cup R^3 \cup R^5 \cup \dots \cup R^{2k+1} \cup \dots$
\end{center}

\begin{theorem}
  $\mathcal{L}$ does not admit strict filtrations.
\end{theorem}

\begin{proof}
  Consider the following frame $\mathcal{F} = \langle W, R \rangle$:

  \xymatrix{
  &&&&& x \ar@(ur,ul) \ar[r] & y \\
  &&&&&& y_1 \ar[r] \ar@/_/[rr] & z_1 \ar[r] & z \ar@(ur,ul)
  }

  Clearly that $\mathcal{F}$ is an $\mathcal{L}$-frame. We define the valuation $\vartheta$ as follows:

  \begin{center}
    $\vartheta(p) = \{ x \}$

    $\vartheta(q) = \{ y, y_1 \}$

    $\vartheta(r) = \{ z \}$
  \end{center}
  Let us put $\Gamma = \operatorname{Sub} \{ p, q, \Diamond r \}$. We factorise $W$ through $\sim_{\Gamma}$ and consider a model $\widehat{\mathcal{M}} = \langle W / \sim_{\Gamma}, \widehat{R}, \widehat{\vartheta} \rangle$, where $\widehat{R} = (\widehat{R}_{min})^{\davidsstar}$.
  We have $(\hat{x}, \hat{z}) \in \widehat{R} \circ \widehat{R} \circ \widehat{R}$, but $\Diamond r$ is not true at $x$.
\end{proof}

@@

The converse implication does not have to true generally. ${\bf GL}$ might be an example of a logic that has the ``finite canonical'' model property with no filtrations.

\section{Fusion stuff}

\begin{defin}
  Let $\mathcal{L}_1$ and $\mathcal{L}_2$ be modal logics, then the fusion $\mathcal{L}_1 * \mathcal{L}_2$ is the minimal bimodal logic that contains $\mathcal{L}_1$ and $\mathcal{L}_2$ \cite{kurucz200715}.
\end{defin}

\begin{theorem}
  $ $

  \begin{enumerate}
  \item ${\bf K}5 * {\bf K}5$ admits definable filtrations.
  \item ${\bf K}5 * \dots * {\bf K}5$ admits definable filtrations.
  \item If $\mathcal{L}_1, \dots, \mathcal{L}_n$ admit strict filtrations, then ${\bf K}5 * \dots * \dots * {\bf K}5 * \mathcal{L}_1 * \dots * \mathcal{L}_n$
  \end{enumerate}
\end{theorem}

  \begin{enumerate}
  \item Let $\Gamma$ be a finite $\operatorname{Sub}$-closed set of bimodal formulas,
  $\mathcal{F} = \langle W, R_1, R_2 \rangle$ a ${\bf K}5 * {\bf K}5$-frame, and $\vartheta$ a valuation on $\mathcal{F}$. Denote $\langle \mathcal{F}, \vartheta \rangle$ as $\mathcal{M}$.

  We introduce the set of fresh variables $V = \{ p_{\psi} \: | \: \psi \in \Gamma \}$ and define a new model $\mathcal{M}' = \langle \mathcal{F}, \vartheta' \rangle$ as follows:
  \begin{center}
    For all $\psi \in \Gamma$, $\mathcal{M}, x \models \psi \Leftrightarrow \mathcal{M}', x \models \psi \Leftrightarrow \mathcal{M}', x \models p_{\psi}$.
  \end{center}

  Consider these modifications of $\Gamma$ and $V$:

  \begin{center}
    $\Gamma' = \Gamma \cup \{ \Diamond_1 \Box_1 \psi \: | \: \Box_1 \psi \in \Gamma \} \cup \{ \Diamond_2 \Box_2 \psi \: | \: \Box_2 \psi \in \Gamma \}$

    $\Delta_1 = V \cup \operatorname{Sub}(\{ \Diamond \Box p_{\psi} \: | \: \Box_1 \psi \in \Gamma \})$

    $\Delta_2 = V \cup \operatorname{Sub}(\{ \Diamond \Box p_{\psi} \: | \: \Box_2 \psi \in \Gamma \})$
  \end{center}
  Let us define equivalence relations $\sim_1$ and $\sim_2$ induced by $\Delta_1$ and $\Delta_2$ respectively.

  Consider $\mathcal{M}_i = \langle W, R_i, \vartheta' \rangle$, a reduct of $\mathcal{M}'$, we have:
  \begin{enumerate}
    \item $\mathcal{M}_i, x \models \Box p_{\psi}$ iff $\mathcal{M}, x \models \Box_i \psi$
    \item $\mathcal{M}_i, x \models \Diamond \Box p_{\psi}$ iff $\mathcal{M}, x \models \Diamond_i \Box_i \psi$
  \end{enumerate}
  So $\sim_i = \sim_{\Gamma'}$ by the construction. Let us put $\widehat{W} = W / \sim_{\Gamma'}$.

  \begin{claim}
    Let $\widehat{R}_i = (R^{min}_{\Delta_i})^{E}$ and
    $\widehat{\vartheta(p)} = \{ [x]_{\sim_i} \: | \: \mathcal{M}_i, x \models p \}$ for $p \in \Delta_1$, define $\widehat{\mathcal{M}}_i = \widehat{W}, \widehat{R}_i, \widehat{\vartheta}$. Then $\widehat{\mathcal{M}}_i \models {\bf K}5$ and $\widehat{\mathcal{M}}_i$ is a filtration of $\mathcal{M}_i$ through $\Delta_i$.
  \end{claim}
  \begin{proof}
    Let us show that $\widehat{R}_i \subseteq R^{max}_{\Delta_i}$ by induction.
    Let $\hat{x} \widehat{R}_i \hat{y}$ such that $\mathcal{M}_i, x \models \Box p_{\psi}$.
    We need $\mathcal{M}_i, y \models p_{\psi}$.
    Recall that $\widehat{R}_i$ is defined inductively as:
    \begin{enumerate}
      \item $R_{\Delta_i}^{0} = R_{\Delta_i}^{min}$
      \item $R_{\Delta_i}^{n + 1} = R_{\Delta_i}^{n} \cup ({R_{\Delta_i}^{n}}^{-1} \circ R_{\Delta_i}^{n})$
      \item $(R^{min}_{\Delta_i})^{E} = \bigcup_{k < \omega} R_{\Delta_i}^{k}$
    \end{enumerate}

    \begin{enumerate}
      \item $n = 0$. This is obvious.
      \item $m = n + 1$. Suppose the statement holds for $R_{\Delta_i}^{n}$, we also have $(\hat{x}, \hat{y}) \in R_{\Delta_i}^{n} \cup ({R_{\Delta_i}^{n}}^{-1} \circ R_{\Delta_i}^{n})$.
      If $(\hat{x}, \hat{y}) \in R_{\Delta_i}^{n}$, then we just apply IH.

      $(\hat{x}, \hat{y}) \in {R_{\Delta_i}^{n}}^{-1} \circ R_{\Delta_i}^{n} \in R_{\Delta_i}^{n}$, then there exists $\hat{z}$ such that $(\hat{z}, \hat{x}) \in R_{\Delta_i}^{n}$ and $(\hat{z}, \hat{y}) \in R_{\Delta_i}^{n}$.

      We rewrite $(\hat{z}, \hat{x}) \in R_{\Delta_i}^{n}$ as the following sausage (for some $\widehat{u_1},  \widehat{u_2}, \dots, \widehat{u_{n - 1}}, \widehat{u_{n}}$):

\xymatrix{
&&& \hat{z} & \ar[l]_{R_{\Delta_i}^{min}} \ar[r]^{R'} \widehat{u_1} & \ar[r]^{R'} \widehat{u_2} \ar[r]^{R'} & \dots & \ar[r]^{R'} \widehat{u_{n - 1}} \ar[r]^{R'} & \widehat{u_{n}} \ar[r]^{R_{\Delta_i}^{min}} & \hat{x}
}
\vspace{\baselineskip}

where $R'$ is either $R_{\Delta_i}^{min}$ or its converse. We clearly have $\mathcal{M}, z \models \Box p_{\psi}$, since $\mathcal{M}, x \models \Box p_{\psi}$ implies $\mathcal{M}, u_{n} \models \Diamond \Box p_{\psi}$. After that we apply the following property of ${\bf K}5$-models:
\begin{center}
  For each $a, b \in M_i$ such that $a R_i b$ we have $\mathcal{M}_i, a \models \Diamond \Box p_{\psi}$ iff $\mathcal{M}_i, b \models \Diamond \Box p_{\psi}$
\end{center}
Then $\mathcal{M}_i, y \models p_{\psi}$ by IH.
    \end{enumerate}
  \end{proof}

  Finally, we consider a model $\widehat{\mathcal{M}} = \langle \widehat{W}, \widehat{R}_1, \widehat{R}_2, \vartheta \rangle$, where $\widehat{R_{\Gamma'}}_i = {{R_i}^{min}_{\Gamma'}}^E$ and $\vartheta(p)$ is defined as usual for $p \in \Gamma$. $\widehat{\mathcal{M}}$ is a filtration of $\mathcal{M}$ through $\Gamma'$.

  Let $\hat{x} \widehat{R_{\Gamma'}}_i \hat{y}$ and $\mathcal{M}, x \models \Box_i \psi$ for $\Box_i \psi \in \Gamma$. Then $\mathcal{M}_i, x \models \Box p_{\psi}$, so $\widehat{\mathcal{M}_i}, \hat{x} \models \Box p_{\psi}$.
  By the claim above, $\widehat{\mathcal{M}_i}$ is a filtration of $\mathcal{M}_i$ through $\Delta_i$, so $\mathcal{M}_i, y \models p_{\psi}$. Then $\mathcal{M}, y \models \psi$.

  \item Likewise
  \item
  \end{enumerate}
\end{proof}

\begin{theorem}
  Let $\mathcal{L}_1$ and $\mathcal{L}_2$ be modal logics such that $\operatorname{Fr}(\mathcal{L}_1)$ and $\operatorname{Fr}(\mathcal{L}_2)$ admit filtrations, so does $\operatorname{Fr}(\mathcal{L}_1 * \mathcal{L}_2$).
\end{theorem}

\begin{proof}

\end{proof}

### 2021-05-30 frp-paper/Paper.tex
filtrations for K5 * K5

\subsection{Axiomatisating ${\bf R}(+, ;)$}

@@

      $\forall$ picks nodes $x, y \in V_n$ and $d, e \in \mathcal{A}$ such that $c \leq d ; e$ for $c \in l_n(x, y)$. $\exists$ has to find a witness. She has to find a $z$ which is either a fresh node or an old one. If $z$ is fresh, then she defines the prenetwork $T$, the edges of which are $x, y, z$ with the labelling:
      \begin{enumerate}
        \item $l_T(x, z) = \up{d}$
        \item $l_T(z, y) = \up{e}$
      \end{enumerate}
      If $z$ is already an element of $\mathcal{A}$, then her response is similar.
      For her response, $\exists$ plays $N_{n + 1} = N_n \cup T$
      \item ({\bf Join move}):

      $\forall$ picks nodes $x, y \in V_n$ and $c + d$ for $c, d \in \mathcal{A}$. $\exists$ has the following two alternatives for her response:
      \begin{enumerate}
        \item $\exists$ chooses $c$ and responds with the prenetwork $\mathcal{N}_{n + 1} = \langle V_{n + 1}, E_{n + 1}, l_{n + 1} \rangle$, where $l_{n+1}(x, y) = \up{(l_n(x,y) \cup \{ c \})}$.
        \item $\exists$ chooses $b$. The response is similar but $l_{n + 1}(x, y) = \up{(l_n(x,y) \cup \{ d \})}$.
      \end{enumerate}
    \end{enumerate}
  \end{enumerate}

  $\forall$ wins the play if there exists $b \leq a$ such that $b \in \mathcal{A}$ such that $b \in l_{\mathcal{N}_i}(x,y)$ for some $i < n$. Otherwise, $\exists$ wins the play.

@@

  \begin{enumerate}
    \item Let $h : \mathcal{A} \to 2^{D \times D}$ is a representation of the base set $D \neq \emptyset$. $\exists$ maintains a map ${}^{'} : \operatorname{Nodes}(\mathcal{N}) \to D$, where $\mathcal{N}$ is a network being played, such that $(x',y') \in h(a)$ iff $\up a \subseteq l_{\mathcal{N}}(x,y)$.

@@

\begin{definition}
  A \emph{term network} is a finite network $\langle V, E, l \rangle$, where $\langle V, E \rangle$ is a directed graph and $l : E \to 2^{Term}$ is a labelling function such that every $l_(x,y)$ is finite for each $(x, y) \in E$.
\end{definition}

@@

Let $\mathcal{N} = \langle V, E, l \rangle$ a term network, $\mathcal{A}$ be a join-semilattice ordered semigroup and $\vartheta : \operatorname{Var} \to {\mathcal{A}}$ a valuation. Let us define the prenetwork $\mathcal{N}^{\vartheta}$ with the same edges and vertices with labelling $l^{\vartheta}(x, y) = \bigcup \{ F \in \operatorname{Up}(\mathcal{A}, \leq) \: | \: l_{\mathcal{N}}(x, y) \subseteq F \}$.

@@

$\mathcal{N} = \langle V, E, l \rangle$ be a $\mathcal{A}$-network and $\mathcal{A}$ is finite. Define the following equivalence relation on $E \times E$ for $(x_1, y_1), (x_2, y_2) \in E$:
\begin{center}
  $(x_1, y_1) \equiv (x_2, y_2)$ iff $l_{\mathcal{N}}(x_1, y_1) = l_{\mathcal{N}}(x_2, y_2)$
\end{center}
If $A$ is finite, then $E /_{\equiv}$ is finite as well since the set $\operatorname{Up}(\mathcal{A}, \leq)$ is finite.

Let us construct the following $\mathcal{A}$-prenetwork $\mathcal{N}_{\equiv} = \langle V_{\equiv}, E /_{\equiv}, l \rangle$ such that:
\begin{enumerate}
  \item $V_{\equiv} = \bigcup \{ \{ x, y \} \: | \: [x,y]_{\equiv} \in E /_{\equiv} \}$, that is, the union of two element sets $\{ x, y \}$ such that there exists an edge $(x,y)$ up to $\equiv$.
  \item $l([x,y]_{\equiv}) = l_{\mathcal{N}}(x,y)$
\end{enumerate}

\begin{lemma} Let $\mathcal{A}$ be a finite join semilattice-ordered semigroup and $\mathcal{N} = \langle V, E, l \rangle$ an $\mathcal{A}$-prenetwork.
  \begin{enumerate}
  \item Let $a \in \mathcal{A}$, then $a \in l_{\mathcal{N}}(x,y)$ iff $a \in l([x,y]_{\equiv})$.

  \item Let $\mathcal{A}$ be a finite join semilattice-ordered semigroup and $\mathcal{N}$ an $\mathcal{A}$-prenetwork. If $\mathcal{A}$ is a network, so is $\mathcal{N}_{\equiv}$. Moreover, $\mathcal{N}_{\equiv}$ is finite.
\end{enumerate}
\end{lemma}

\begin{proof}
$ $
  \begin{enumerate}
  \item If $a \in l_{\mathcal{N}}(x,y)$, suppose $(x_1,y_1) \equiv (x,y)$, so $l_{\mathcal{N}}(x,y) = l_{\mathcal{N}}(x_1,y_1)$, then $a \in l_{\mathcal{N}}(x_1,y_1)$. Therefore, $a \in l([x,y]_{\equiv})$. The converse implication is obvious.
  \item Follows from the definition of a network and the fact that the proof does not depend on the choice of equivalence classes representatives.
  Let us check join-primeness as an example. The rest of the cases are considered in a similar fashion:
  Let $a, b \in \mathcal{A}$ and $x, y \in V$ such that $a + b \in l([x,y]_{\equiv})$.
  Then $a + b \in l(x,y)$ in the original network. Then we have either $a \in l(x,y)$ or $b \in l(x,y)$ by the join-primeness condition. Therefore, either $a \in l([x,y]_{\equiv})$ or $b \in l([x,y]_{\equiv})$

  $\mathcal{N}_{\equiv}$ is finite since $E_{\equiv}$ is finite. That makes $V_{\equiv}$ finite as well.
  \end{enumerate}
\end{proof}

\begin{theorem}\label{frpjoin}
  ${\bf R}(+, ;)$ has the finite representation property.
\end{theorem}

\begin{proof}
  Let $\mathcal{A} \in {\bf R}(+, ;)$ and $\mathcal{A}$ is finite.
  Let us show that $\mathcal{A}$ has a representation over a finite base.
  We already know that $\exists$ has a winning strategy on $\mathcal{G}^{\omega}(\mathcal{A})$, so we have $\mathcal{N}$, the resulting network. So $\mathcal{N}_{\equiv}$ is a finite network by the previous lemma.
  Define the following map $f : \mathcal{A} \to 2^{E_{\equiv}}$ as follows:
\begin{center}
  $f : a \mapsto \{ (x,y) \: | \: \exists b \leq a \: \& \: b \in l([x,y]_{\equiv}) \}$.
\end{center}
$f$ preserves all operations and it is injective for the same reason as $\operatorname{rep}$ constructed above. Let us check that.

If $(x,y) \in f(a + b)$, then there is $c \leq a + b$ such that $c \in l([x,y]_{\equiv})$, then $c \in l_{\mathcal{N}}(x,y)$, so we have either $a \in l_{\mathcal{N}}(x,y)$ or $b \in l_{\mathcal{N}}(x,y)$. Thus, either $a \in l([x,y]_{\equiv})$ or $b \in l([x,y]_{\equiv})$.
If $(x, y) \in f(a)$, then there exists $c \leq a$ such that $c \in l([x,y]_{\equiv})$, but $a + b \in \in l([x,y]_{\equiv})$. Therefore, $f(a + b) = f(a) \cup f(b)$.

If $(x,y) \in f(a ; b)$, then there exists $c \leq a ; b$ with $c \in l([x,y]_{\equiv})$, then $c \in l_{\mathcal{N}}(x,y)$. By the saturation condition, there is $z \in \operatorname{Nodes}(\mathcal{N})$ with $a \in l_{\mathcal{N}}(x,z)$ and $b \in l_{\mathcal{N}}(z,y)$.
Then $a \in l([x,z]_{\equiv})$ and $b \in l([z,y]_{\equiv})$.
If $(x,y) \in f(a);f(b)$, then there is $z \in V_{\equiv}$ with $(x, z) \in f(a)$ and $(z, y) \in f(b)$, then there are $c$ and $d$ with $c \leq a$ and $c \in l([x,z]_{\equiv})$ and $d \leq b \in l([z,y]_{\equiv})$ respectively. Then $c ; d \in l([x,y]_{\equiv})$ by the saturation condition.

Suppose $a \neq b$, so we have either $a \not\leq b$ or $b \not\leq a$.
Suppose $a \not\leq b$. Let $(x, y) \in f(a)$, then there is $c \leq a$ with $c \in l([x,y]_{\equiv})$, then $c \in l_{\mathcal{N}}(x,y))$ and, moreover, $c \in l_{\mathcal{N}^{*}(a,b)}(x,y))$.
We know that $\exists$ has a winning strategy in $\mathcal{G}_{\omega}(\mathcal{A})$, so
$b \notin l_{\mathcal{N}^{*}(a,b)}(x,y))$. So $b \notin l([x,y]_{\equiv})$ and $f(a) \neq f(b)$.
The second alternative is similar to the previous one.

The base set of a representation, $V /_{\equiv}$, is finite, see the previous lemma.
\end{proof}

In turn, the finite representation property and the presence of a recursively enumerable axiomatisation imply the following corollary.

\begin{corollary}
  The problem of membership to ${\bf R}(;, +)$ is decidable for finite structures.
\end{corollary}

\begin{proof}
  Follows from Proposition~\ref{dec}, Theorem~\ref{axiomatisation}, and Theorem~\ref{frpjoin}.
\end{proof}

>>>>

\subsection{Axiomatising ${\bf R}(+, ;)$}

@@

      $\forall$ picks an edge $(x, y) \in E_n$ and $d, e \in \mathcal{A}$ such that $c \leq d ; e$ for $c \in l_n(x, y)$. $\exists$ has to find a witness. She has to find a $z$ which is either a fresh node or an old one. If $z$ is fresh, then she defines the prenetwork $T$, the edges of which are $x, y, z$ with labelling:
      \begin{enumerate}
        \item $l_T(x, z) = \up{d}$
        \item $l_T(z, y) = \up{e}$
      \end{enumerate}
      If $z$ is already an element of $\mathcal{A}$, then her response is similar.
      For her response, $\exists$ plays $N_{n + 1} = N_n \cup T$
      \item ({\bf Join move}):

      $\forall$ picks an edge $(x, y) \in E_n$ and $c + d$ for $c, d \in \mathcal{A}$. $\exists$ has the following two alternatives for her response:
      \begin{enumerate}
        \item $\exists$ chooses $c$ and responds with the prenetwork $\mathcal{N}_{n + 1} = \langle V_{n + 1}, E_{n + 1}, l_{n + 1} \rangle$, where $l_{n+1}(x, y) = \up{(l_n(x,y) \cup \{ c \})}$.
        \item $\exists$ chooses $b$. The response is similar but $l_{n + 1}(x, y) = \up{(l_n(x,y) \cup \{ d \})}$.
      \end{enumerate}
    \end{enumerate}
  \end{enumerate}

  $\forall$ wins the play if $b \notin l_{\mathcal{N}_i}(x,y)$ for some $i < n$. Otherwise, $\exists$ wins the play.

@@

  \begin{enumerate}
    \item Let $h : \mathcal{A} \to 2^{D \times D}$ is a representation of the base set $D \neq \emptyset$. $\exists$ maintains a map ${}^{'} : \operatorname{Nodes}(\mathcal{N}) \to D$, where $\mathcal{N}$ is a network being played, such that $a \in l_{\mathcal{N}}(x,y)$ implies $(x',y') \in h(a)$.

@@

\begin{definition}
  A \emph{term network} is a finite network $\langle V, E, l \rangle$, where $\langle V, E \rangle$ is a directed graph and $l : E \to 2^{Term}$ is a labelling function such that every $l(x,y)$ is finite for each $(x, y) \in E$.
\end{definition}

@@

Let $\mathcal{N} = \langle V, E, l \rangle$ a term network, $\mathcal{A}$ be a join-semilattice ordered semigroup and $\vartheta : \operatorname{Var} \to {\mathcal{A}}$ a valuation. Let us define the prenetwork $\mathcal{N}^{\vartheta}$ with the same edges and vertices with labelling $l^{\vartheta}(x, y) = \up \vartheta[l_{\mathcal{N}}(x, y)]$.

@@

\begin{definition}
  Let $\mathcal{A}$ be a join semilattice-ordered semigroup and let $\mathcal{N}_1$ and $\mathcal{N}_2$ be $\mathcal{A}$-networks. A strong homomorphism from $\mathcal{N}_1$ onto $\mathcal{N}_2$ is a map $f : \mathcal{N}_1 \twoheadrightarrow \mathcal{N}_2$ such that:
  \begin{enumerate}
    \item $(x, y) \in E_2$ implies $(f(x), f(y)) \in E_1$,
    \item If $(x', y') \in E_2$, then there exists $x, y \in E_1$ such that $f(x) = x'$ and $f(y) = y'$ and $(x, y) \in E_1$,
    \item $l_{\mathcal{N}_1}(x, y) = l_{\mathcal{N}_2}(f(x),f(y))$
  \end{enumerate}
  By $\mathcal{N}_1 \twoheadrightarrow \mathcal{N}_2$ we mean that there exists a strong homomorphism of $\mathcal{N}_1$ onto $\mathcal{N}_2$.
\end{definition}

\begin{lemma}
  Let $\mathcal{A}$ be a representable join semilattice-ordered semigroup and $\mathcal{N} = \langle V, E, l \rangle$ and $\mathcal{N}' = \langle V', E', l' \rangle$ $\mathcal{A}$-networks.

  Suppose $\mathcal{N} \twoheadrightarrow \mathcal{N}'$. If $\mathcal{N}^{*}$ is a representation of $\mathcal{A}$, so is $ $
\end{lemma}

\begin{lemma}
\end{lemma}
